Technology-based aids for people affected by Autism Spectrum Disorder (ASD)

### 2017-11-22 paper.tex
Commit di prova per usare git

Results show that the discriminating ability of nearest neighbor classifier over STFT-BW is satisfactory (0.967 for the F3 electrode) and table \ref{tab:prediction} shows a $89.5 \%$ probability of correct classification through  STFT-BW.
Moreover, figure \ref{fig:head} shows the obtained results for the three frequency bands alpha beta and gamma: coherence values that show meaningful differences with $p < 0.05 $ are represented through dot lines, while differences with $p < 0.01$ are represented through solid lines: the resulting observation is that there are more abnormalities in connectivity for the left temporal lobe than the other ones, observation that sticks with the assumption of a correlation between \gls{asd} syndrome and abnormal behavior of temporal lobes \cite{Zilbovicius2000} \cite{ANA}.

>>>>

Results show that the discriminating \cri{Commento prova per usare git} ability of nearest neighbor classifier over STFT-BW is satisfactory (0.967 for the F3 electrode) and table \ref{tab:prediction} shows a $89.5 \%$ probability of correct classification through  STFT-BW.
Moreover, figure \ref{fig:head} shows the obtained results for the three frequency bands alpha beta and gamma: coherence values that show meaningful differences with $p < 0.05 $ are represented through dot lines, while differences with $p < 0.01$ are represented through solid lines: the resulting observation is that there are more abnormalities in connectivity for the left temporal lobe than the other ones, observation that sticks with the assumption of a correlation between \gls{asd} syndrome and abnormal behavior of temporal lobes \cite{Zilbovicius2000} \cite{ANA}.
